%! Author = cnatzke
%! Date = 05/24/2022
\documentclass[cnatzke_thesis_proposal.tex]{subfiles}
\usepackage{amssymb}
\begin{document}
%\chapter{Introduction}
%%%%%%%%%%%%%%%%%%%%
    \subsection{Nuclear Equation of State}
%%%%%%%%%%%%%%%%%%%%
The Nuclear Equation of State (EOS) governs the properties of nuclear matter and defines the properties of neutron-rich nuclei, the structure of neutron stars, supernova explosions and compact object mergers. \cite{Kaufmann2020} The EOS is well constrained for symmetric nuclear matter, matter where the number of protons and neutrons are roughly equal, but the properties for neutron rich matter require further investigation. \cite{Danielewicz2002} 
The properties of interest are encoded in the nuclear symmetry energy $S(n)$ and the slope parameter $L$. Atomic nuclei provide a terrestrial system to study the slope parameter using the neutron-skin thickness, the difference between the point-neutron and point-proton radii, mathematically denoted as $R_{skin} = R_n - R_p$. \cite{Tsang2012} A direct experimental measurement of $R_{skin}$ is extremely challenging and can be extracted by its correlation to collective isovector observables at low energies. \cite{Birkhan2017} One such observable is the dipole polarizability $\alpha_D$ \cite{Birkhan2017}.

%%%%%%%%%%%%%%%%%%%%
\subsection{Electric Polarizability and Magnetic Susceptibility}
%%%%%%%%%%%%%%%%%%%%

Nuclear DFT calculations suggest a strong correlation between $\alpha_D$ and the neutron radius \cite{hagen_neutron_2016}, $R_{n}$. 
Polarizability is a fundamental concept in physics the describes how applied electric or magnetic fields induce an electric or magnetic dipole, or higher-order multipole, moment in the matter of interest.\cite{jackson_classical_1999} The concept of polarizability plays a large role in nuclear physics observables across a broad range of interests. For example the static dipole polarization of the ground and excited state shape of atomic nuclei is influenced by the state's coupling to higher-energy collective modes, like the giant dipole resonance and pygmy dipole resonance, via virtual excitations. As described in \cite{soderstrom_electromagnetic_2020}, the static dipole polarizability, $\alpha_D$ can be obtained from the photonuclear population of excited states, given by

\begin{equation} \label{eqn:scalar_dipole_polarizability}
    \alpha_{D,E1} = 2 e \sum_n \frac{|\langle I_0 || E1 || I_n \rangle |^2}{E_n - E_0}
\end{equation}

where $I_0$, $E1$, and $I_n$ are the matrix elements for the ground state, electric dipole transition, and excited state respectively; $e$ is the elementary charge of the electron; and $E_n$ is the energy of the state. 
The value of $alpha_D$, and the analogous magnetic susceptibility $\chi$, in atomic and nuclear systems spans many orders of magnitude depending on the scale of interest, for example the magnetic susceptibility of a nucleus is twelve orders of magnitude smaller than that of an atom. \cite{knupfer_scaling_1985}

Following the explanation in \cite{soderstrom_electromagnetic_2020} the polarizability can be expanded past the scalar case to include separate tensor components describing higher-order electric and magnetic multipoles. Using the nuclear structure framework these off diagonal polarizabilities appear as very weak second-order electromagnetic processes that can be expressed analogously to Eq. (\ref{eqn:scalar_dipole_polarizability}) in terms of either electric and magnetic components or different multipolarities. 

\begin{equation} \label{eqn:m2e2_dipole_polarizability}
    \alpha_{M2E2} = \sum_n \frac{\langle I_f || E2 || I_n \rangle \langle I_n || M2 || I_i \rangle}{E_n - \omega}
\end{equation}

or 

\begin{equation} \label{eqn:m2e2_dipole_polarizability}
    \alpha_{E3M1} = \sum_n \frac{\langle I_f || M1 || I_n \rangle \langle I_n || E3 || I_i \rangle}{E_n - \omega}
\end{equation}

where $\omega$ is the interference frequency of the emitted gamma-rays and is approximated to one half of the initial energy. 
This second-order electromagnetic process was discussed in the doctorate dissertation of Maria G\"oppert-Mayer \cite{goppert-mayer_uber_1931} where the estimated relative probability of two-photon absorption to the single-photon process is $10^{-7}$. 

The electric dipole polarizability has been measured for a variety of stable isotopes, $^{48}$Ca \cite{Birkhan2017}, $^{120}$Sn \cite{Hashimoto2015}, and $^{208}$Pb \cite{Tamii2011} using proton inelastic scattering, and $\alpha_D$ has only been measured for one short-lived nucleus, $^{68}$Ni. \cite{Rossi2013}
At this time the electric dipole polarizability for a short lived nuclear state has not been experimentally measured, but using the \textit{transition} electric polarizabilty, the difference in $\alpha_D$ between the two states, and the ground state polarizabilty the polarizabilty of a short-lived nuclear state can be measured.

%%%%%%%%%%%%%%%%%%%%
\subsection{Nuclear Gamma Decay and Internal Conversion}
%%%%%%%%%%%%%%%%%%%%
Nuclear gamma decay is an electromagnetic process in which an unstable nucleus deexcites into a more energetically favourable state via the emission of a photon of gamma radiation. The kinetic energy of the photon is equivalent to the energy difference in the initial and final states of the nucleus, save for a small amount of recoil kinetic energy imparted to the nucleus, and the photon's angular momentum equals the difference in angular momentum of the nucleus' state. This restriction on angular momentum forbids the emission of a gamma-ray from two states with equal angular momentum, a photon must have at least 1$\hbar$ unit of angular momentum, denoted as an E0 transition.

Gamma-decay often competes with another first-order decay mode called Internal Conversion. Internal conversion (IC) is an electroweak process where the nucleus deexcites by transferring its energy to an atomic electron. Internal Conversion is particularly important for transitions where both the initial and final states have a $0^+$ spin-parity since IC is the only direct process by which the nucleus can deexcite. \cite{Krane1988} 

%%%%%%%%%%%%%%%%%%%%
\subsection{Nuclear Two-photon Decay}
%%%%%%%%%%%%%%%%%%%%

The only known experimental probe for the transition electric dipole polarizabilty, $\alpha_D^{fi}$ is nuclear two-photon decay.
Nuclear two-photon decay is a second-order QED process wherein the nucleus simultaneously emits two photons of continuous energy that sum to the initial excitation energy, and the two photons couple to preserve the change in angular momentum of the transition. \cite{Kramp1987} 

Nuclear two-photon decay is a fully competitive process, albeit second-order, and can occur between any two states in the nucleus making it difficult to measure for transitions where single gamma decay is allowed. Recently competitive two-photon decay has been measured in $^{137m}$Ba \cite{soderstrom_electromagnetic_2020} but is more easily observed in nuclei that have $0^+$ ground and first excited states since the only allowed decay modes for E0 transitions are internal conversion and two-photon decay. 

E0 two-photon decay, called non-competitive two-photon decay, has been observed in $^{16}$O, $^{40}$Ca \cite{schirmer_double_1984}, and $^{90}$Zr \cite{schirmer_double_1984} using dedicated scintillator arrays.   


%%%%%%%%%%%%%%%%%%%%
\end{document}
%%%%%%%%%%%%%%%%%%%%
